%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Artem I. Yankov} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

%\moveleft.5\hoffset\centerline{yankovai@umich.edu}
%\moveleft.5\hoffset\centerline{\textbf{LinkedIn}: https://www.linkedin.com/in/artemyankov}
%\moveleft.5\hoffset\centerline{\textbf{GitHub}: https://github.com/yankovai}
\moveleft.5\hoffset\centerline{\textbf{Phone}: (401) 206-9133}
\moveleft.5\hoffset\centerline{\textbf{Email}: yankovai@umich.edu}
\moveleft.5\hoffset\centerline{\textbf{Address}: 4502 42nd Ave SW, Apt 606, Seattle WA 98116}
\moveleft.5\hoffset\centerline{\textbf{Personal Website}: www.1oclockbuzz.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------

\section{TECHNICAL SKILLS} 

{\sl Languages:} Python, SQL, R, bash, Fortran, \LaTeX \\
{\sl Operating Systems:} OS X, Unix, Windows \\
{\sl Applications \& Libraries:} Tableau, AWS, Spark, SciKit-Learn, Pandas, git  \\
{\sl Other Skills:} Machine learning, data mining, uncertainty quantification, numerical linear algebra

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Data Scientist} \hfill July 2015 - Present\\
Rover.com, Seattle, WA

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Improved matching between dog sitters and owners in the core search rank algorithm by implementing Bayesian updating rules.
\end{itemize}

{\sl Data Scientist} \hfill August 2014 - July 2015\\
Zillow, Seattle, WA

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Used network graph algorithms and AWS framework to build a zip code recommendation engine for advertisers.  
\item Implemented models to predict customer churn. Developed weekly churn visualizations in Tableau utilized by company CEO to guide pricing decisions. 
\item Used linear programming algorithms to match consumers with mortgage lenders given various geospatial restrictions.
\item Devised metrics and constructed statistical models to analyze the performance of business-to-business marketing efforts.  
\end{itemize}

{\sl Data Scientist Intern} \hfill May 2014 - August 2014 \\
Globys, Seattle, WA

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Developed a simulator for the usage behavior of mobile phone subscribers in a contextual marketing framework using machine learning and statistical data analysis.
\item Researched and developed algorithms for predicting customer churn, including Bayesian Bandits and Hidden Markov Models. 
\end{itemize}

{\sl Graduate Student Research Assistant} \hfill July 2010 - December 2014 \\
University of Michigan, Department of Nuclear Engineering, Ann Arbor, MI

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Applied statistical and machine learning techniques to analyze the phenomenon of fission gas release in nuclear fuel performance. 
\begin{itemize}
\item Involved folding together experimental data and computer simulation results to improve predictive capabilities of computer codes. 
\end{itemize}
\item Research in how uncertainties in reactor simulation code input parameters propagate to output predictions.
\begin{itemize}
\item Extensive collaboration with researchers from Oak Ridge National Laboratory to develop algorithms for quantifying uncertainties in nuclear reactor simulators when faced with large numbers of correlated, stochastic inputs.
\item Results of research published in leading journal and awarded first prize at a major technical conference.
\end{itemize}
\item Implemented numerical linear algebra routines into primary software used by Nuclear Regulatory Commission to simulate nuclear reactor accident scenarios.
\end{itemize}

%----------------------------------------------------------------------------------------
%	DATA SCIENCE PROJECTS SECTION
%----------------------------------------------------------------------------------------

%\section{PERSONAL \\ PROJECTS}
%
%{\sl StackOverflow Query Tag Extraction} 
%
%\begin{itemize} \itemsep -2pt % Reduce space between items
%\item Used Python to analyze over 6,000,000 StackOverflow queries and corresponding tags using MapReduce-type framework.  
%\item Reformulated raw textual data to a useful form and placed into SQL database for further processing.
%\item Developed an algorithm to automatically predict new tags based on similarity to queries in training data set with over 80\% accuracy.
%\end{itemize}
%
%{\sl NCAA College Basketball Prediction} 
%
%\begin{itemize} \itemsep -2pt % Reduce space between items
%\item Scraped a decade's worth of college basketball data from sports-reference.com/cbb using BeautifulSoup and stored results in SQLite database.  
%\item Analyzed data and developed a logistic regression model to predict the outcome of unplayed games with some 14\% lift. 
%\item Ranked all college basketball teams based on simulations of predictive model. 
%\item Created a visualization of predictive model performance using Tableau.
%\end{itemize}
%
%{\sl Twitter User Cravings}
%
%\begin{itemize} \itemsep -2pt % Reduce space between items
%\item Used Twitter Streaming API to investigate cravings of Twitter users. 
%\item Utilized Apache Pig to filter and process relevant data. 
%\item Created a visualization application using Tableau to present results. 
%\end{itemize}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

\textbf{University of Michigan} \hfill Ann Arbor, MI \\
{\sl Ph.D} Nuclear Engineering and Radiological Sciences \hfill December 2014

%\textbf{University of Michigan} \hfill Ann Arbor, MI \\
%{\sl M.S.E.} Nuclear Engineering and Radiological Sciences \hfill January, 2014

\textbf{Rose-Hulman Institute of Technology} \hfill Terre Haute, IN \\
{\sl B.S.} Mathematics \hfill May 2010 \\
{\sl B.S.} Physics \\
Minor: Computational Science \\
Clarence P. Sousley Award for demonstration of exceptional performance in the mathematical sciences.
  
\end{resume}
\end{document}
